Towards understanding the central limit theorem by learning Python basics

### 2021-02-19 paper/article.tex
Fix typo

The other students explained the result $2.5$ by mentioning symmetry, and the same argument was
used for the generalization. But no answer was found to compute the variance, only for one student,
and in that case it was incorrect (see Fig.\ref{52})---clearly, on line 10 something like
\begin{lstlisting}[language=Python,firstnumber=10]
  Varianz = Varianz + (w.count("K")-Erwartungswert)**2
\end{lstlisting}
should have been written. Actually, the notation \texttt{**2} could be something unfamiliar
for those who never did any programming before. Anyway, the result $0.078125$ should have been
suspicious. It is also remarkable that this student preferred the Latin alphabet to Greek characters.
\begin{figure}
\begin{center}\includegraphics[width=1.0\textwidth]{52}
\caption{A student's incorrect program code to compute variance in sheet 5}
\label{52}
\end{center}
\end{figure}

>>>>

The other students explained the result $2.5$ by mentioning symmetry, and the same argument was
used for the generalization. But no answer was found to compute the variance, only for one student,
and in that case it was incorrect (see Fig.~\ref{52})---clearly, on line 10 something like
\begin{lstlisting}[language=Python,firstnumber=10]
  Varianz = Varianz + (w.count("K")-Erwartungswert)**2
\end{lstlisting}
should have been written. Actually, the notation \texttt{**2} could be something unfamiliar
for those who never did any programming before. Anyway, the result $0.078125$ should have been
suspicious. It is also remarkable that this student preferred the Latin alphabet to Greek characters.
\begin{figure}
\begin{center}\includegraphics[width=1.0\textwidth]{52}
\caption{A student's incorrect program code to compute variance in sheet 5}
\label{52}
\end{center}
\end{figure}
